---
title: 'Gov52 Final Project: Replication of "Economic Reasoning with a Racial Hue:
  Is the Immigration Consensus Purely Race Neutral?"'
author: "Will Rowley"
date: "5/8/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
library(tidyverse)
library(haven)
library(foreign)
library(MASS)


knitr::opts_chunk$set(echo = FALSE)
```

```{r data-import}

hhdata <- read_dta("./data/hhdata.dta")

mturk <- read_dta("./data/immigration_mturk.dta")

ssi <- read_dta("./data/immigration_ssi.dta")

```

# Introduction 

## Original Paper Overview

"Economic Reasoning with a Racial Hue: Is the Immigration Consensus Purely 
Race Neutral?" by Newman and Malhotra [1] is an in depth look 
at native US citizen's views on immigration. 
Specifically, it is concerned with a concept called the "skill premium", which
is the preference that native citizens have for high skill workers, such as 
doctors, scientists, and engineers over low skill workers without a higher 
education. The paper states that prior research has shown that in immigrant 
receiving nations [2][3], this skill premium is present, irrespective of the immigrants
nationality, race, or religion, and irrespective of the respondents economic 
position, partisanship, and personal prejudices. 

This is a surprising result,
as one would expect that personal views on immigration would be driven by one's 
own position in the labor market, wanting immigrants that wouldn't compete with
them for jobs. However, there seems to be a consensus that high skilled immigration 
is better for the receiving country, trumping all other cultural and 
ethnic prejudices. 
  This paper seeks to test the idea that the skill premium given to immigrants is 
race neutral. Specifically, in America it looks at aversion to Latino immigration,
the most prevalent group in the US who mostly work at low-skill jobs. The paper
subjects this race neutral assumption to a series of "critical tests", looking
at how a variety of factors such as prejudice and income influence how a person
gives a skill premium to a specific individual. 

- Critical Test 1 - Does racial prejudice condition the skill premium? In other
words, how do individuals with a high level of prejudice view low and high 
skilled immigrants from different countries. 

- Critical Test 2 - Do preexisting sociotropic beliefs about skill condition 
the skill premium? How do preexisting beliefs about high vs. low skilled 
immigrants impact someone's view on a particular low vs. high skilled immigrant
from different countries. 

- Critical Test 3 - Does providing information about the value of low-skilled
immigrant workers attenuate the skill premium? If you show people how low-skilled
immigration is actually good for the country, how do their views change? 

- Critical Test 4 -  Does manipulating skill also manipulate cultural 
attributes? How do respondents view an immigrant, independent of their 
assumption on how well they can assimilate.

This paper concludes that while it can replicate the existence of the skill 
premium, it doesn't find the same race neutrality as previous research. 
Specifically, critical test 1 fails, as the data shows that those with higher 
levels of prejudice value high skilled immigrants more than those with low 
levels of prejudice. Specifically, they care more about whether a hypothetical 
immigrant from Mexico is high skilled than they do for majority white countries,
while those with low prejudice afford the same skill premium to all immigrant, 
independent of country of origin. 

## Our Replication

In our replication project, we work with 3 different data sets. The first is
data collected by Hainmueller and Hopkins, a paper that confirms the existence
of the skill premium. The authors use this data to test for racial bias not 
initially looked at in the original paper. The second two datasets are from 
original experiments designed by Newman and Malhotra, one conducted through 
Amazon's Mechanical Turk and the other through Survey Sampling International. 
The surveys are all constructed in similar ways, asking respondents how likely
they are to admit a particular individual based on that immigrant's 
country of origin, job, gender, age, education, ect. 

The code provided proved largely unhelpful, as none of the meaningful code is 
written in r, and infact is written in a language I have thus be unable to 
identify. It does provide information on what the variables represent, but 
beyond that much of the analysis in this paper is done independent of their
done in their code. 

We perform ordinary least squares regressions as is done in the original paper. 
We look at the likelihood of accepting an immigrant as a function of that 
immigrant's skill, with the respondents subset by their prejudices and 
immigrants subset by their country of origin. We focus on the results of 
critical tests one and two, since these are the tests that challenge the race
neutral assumptions of previous literature. 

# Critical Test 1 - Reproduction with Hainmueller and Hopkins data

We first seek to reproduce the results of figure 1, which shows that in the 
Hainmueller and Hopkins data, there is evidence of racial bias for the skill
premium in high prejudice individuals. We run a ordinary least squares 
regression for different subsets of the population for admitting an immigrant
as a function of that immigrants characteristics, and look at the coefficient
of the immigrants skill (i.e. how much being a high skill immigrant impacts 
their chance of the respondent approving them). We define an individual as 
having high prejudice as someone who responded below 50 on survey question 5, a
question designed to evaluate their prejudice against latino immigrants. 

```{r}

# DATA CLEANING FOR CRITICAL TEST 1

hhdata_clean <- hhdata %>% 
                
  dplyr::select(chosen_immigrant, 
         featjob, 
         w1_q5, 
         featcountry, 
         featgender, 
         featlang, 
         featexp, 
         feated) %>%
  
  drop_na() %>%
  
  # We sort jobs into low skill ones and high skill ones
  
  mutate(jobskill = factor(featjob, labels = c("lowskill",
                                        "lowskill",
                                        "lowskill",
                                        "lowskill",
                                        "lowskill",
                                        "lowskill",
                                        "lowskill",
                                        "highskill",
                                        "highskill",
                                        "highskill",
                                        "highskill"))) %>% 
  
  # Select the countries we care about
  
  filter(featcountry %in% c(1, 2, 3, 5)) %>%
  
  mutate(country = factor(featcountry, labels = c("Germany", 
                                                      "France", 
                                                      "Mexico", 
                                                      "Poland"))) %>%
  
  # define high prejudice as someone with a w1_q5 of under 50

  mutate(prejudice = ifelse(w1_q5 >= 50, "Low", "High"))

# CREATING THE MODELS AND GATHERING THE COEFFICIENTS

ct1 <- data.frame(Country = character(),
                  prejudice = character(), 
                  estimate = double(),
                  se = double())

# Germany Low prejudice

ct1_fit <- glm(chosen_immigrant ~ jobskill, 
              data = hhdata_clean %>% filter(country == "Germany",
                                             prejudice == "Low"),
              family = binomial(link = "logit"))

ct1[nrow(ct1) + 1,] <- c("Germany",
            "Low",
            summary(ct1_fit)$coefficients[2,1],
            summary(ct1_fit)$coefficients[2,2])

# Germany LHigh prejudice

ct1_fit <- glm(chosen_immigrant ~ jobskill + featgender + featlang + featexp + feated, 
              data = hhdata_clean %>% filter(country == "Germany",
                                             prejudice == "High"),
              family = binomial(link = "logit"))


ct1[nrow(ct1) + 1,] <- c("Germany",
            "High",
            summary(ct1_fit)$coefficients[2,1],
            summary(ct1_fit)$coefficients[2,2])

# France Low prejudice

ct1_fit <- glm(chosen_immigrant ~ jobskill + featgender + featlang + featexp + feated, 
              data = hhdata_clean %>% filter(country == "France",
                                             prejudice == "Low"),
              family = binomial(link = "logit"))


ct1[nrow(ct1) + 1,] <- c("France",
            "Low",
            summary(ct1_fit)$coefficients[2,1],
            summary(ct1_fit)$coefficients[2,2])


# France High prejudice

ct1_fit <- glm(chosen_immigrant ~ jobskill + featgender + featlang + featexp + feated, 
              data = hhdata_clean %>% filter(country == "France",
                                             prejudice == "High"),
              family = binomial(link = "logit"))


ct1[nrow(ct1) + 1,] <- c("France",
            "High",
            summary(ct1_fit)$coefficients[2,1],
            summary(ct1_fit)$coefficients[2,2])

# Poland Low prejudice

ct1_fit <- glm(chosen_immigrant ~ jobskill + featgender + featlang + featexp + feated, 
              data = hhdata_clean %>% filter(country == "Poland",
                                             prejudice == "Low"),
              family = binomial(link = "logit"))


ct1[nrow(ct1) + 1,] <- c("Poland",
            "Low",
            summary(ct1_fit)$coefficients[2,1],
            summary(ct1_fit)$coefficients[2,2])

# Poland High prejudice

ct1_fit <- glm(chosen_immigrant ~ jobskill + featgender + featlang + featexp + feated, 
              data = hhdata_clean %>% filter(country == "Poland",
                                             prejudice == "High"),
              family = binomial(link = "logit"))


ct1[nrow(ct1) + 1,] <- c("Poland",
            "High",
            summary(ct1_fit)$coefficients[2,1],
            summary(ct1_fit)$coefficients[2,2])

# Mexico Low prejudice

ct1_fit <- glm(chosen_immigrant ~ jobskill + featgender + featlang + featexp + feated, 
              data = hhdata_clean %>% filter(country == "Mexico",
                                             prejudice == "Low"),
              family = binomial(link = "logit"))


ct1[nrow(ct1) + 1,] <- c("Mexico",
            "Low",
            summary(ct1_fit)$coefficients[2,1],
            summary(ct1_fit)$coefficients[2,2])

# Mexico Low prejudice

ct1_fit <- glm(chosen_immigrant ~ jobskill + featgender + featlang + featexp + feated, 
              data = hhdata_clean %>% filter(country == "Mexico",
                                             prejudice == "High"),
              family = binomial(link = "logit"))


ct1[nrow(ct1) + 1,] <- c("Mexico",
            "High",
            summary(ct1_fit)$coefficients[2,1],
            summary(ct1_fit)$coefficients[2,2])

# GRAPH

ct1 <- ct1 %>%
  
  mutate(estimate = as.double(estimate)) %>% 
  
  mutate(se = as.double(se)) %>%
  
  mutate(lb = (estimate - (1.96 * se))) %>%
  
  mutate(ub = (estimate + (1.96 * se)))

ct1 %>%
  
  group_by(prejudice, Country) %>%
  
  ggplot() +
  
  geom_pointrange(aes(x = prejudice, 
             y = estimate, 
             ymin = lb, 
             ymax = ub, 
             shape = Country,
             fill = Country),
             position = position_dodge(width=.5),
             size = 1) + 
  
  geom_hline(yintercept=0) + 
  
  labs(x = "Prejudice Level",
       y = "Skill Premium Afforded",
       title = "Critical Test 1 Analysis with HH Data") + 
  
  theme_classic()


```

While our models return different coefficients then the original paper, the 
end analysis is the same, in that prejudice against Mexican immigrants confers
a higher skill premium. In other words, those with aversions to Latino 
immigrants care more about that immigrant's skill level when deciding whether
they support them immigrating, more so than low prejudice individuals. 
Furthermore, this result is statistically significant, with 95% error bars shown
on the graph. For white majority countries, this result is not statistically 
significant, with the trend being the opposite for Germany. 

# Critical Test 1 with Mechanical Turk Data

The mechanical turk data was the first dataset collected by the researchers. 
It operates similarly to the Hainmueller and Hopkins survey, with respondents
being asked to report the likelihood of approving of an individual's
immigration depending on that individuals country of origin, skill level, and 
other factors. We define low and high prejudice individuals based on their 
average of survey questions that asked their opinions on hispanics being 
"intelligent, illegal, lazy, and violent", with the bottom 50% of individuals
being identified as high prejudice and the rest low. We then run similar 
regressions as those in the previous section. 

```{r}

ct1_mturk <- mturk %>% 
  
  mutate(hisp_prej = (hispilleg + hispintel + hisplazy + hispviol) / 4) %>%
  
  mutate(white_prej = (whiteilleg + whiteintel + whitelazy + whiteviol) / 4) %>%
  
  dplyr::select(acceptscale_01, skill, info, white_prej, hisp_prej, country) %>%
  
  mutate(country = factor(country, labels = c("Canada", "Mexico"))) %>%
  
  drop_na() %>%
  
  # we define high hisp prejudice to be below 3.5
  
  mutate(hisp_prej = ifelse(hisp_prej <= 3, "High", "Low")) %>%
  
  mutate(skill = factor(skill, labels = c("Low", "High"))) 

  
ct1_mturk_co <- data.frame(Country = character(),
                  prejudice = character(), 
                  estimate = double(),
                  se = double())

# mexico high prej

ct1_mturk_fit <- glm(acceptscale_01 ~ skill,
                       data = ct1_mturk %>% filter(country == "Mexico",
                                             hisp_prej == "High",
                                             info == 0))

ct1_mturk_co[nrow(ct1_mturk_co) + 1,] <- c("Mexico",
                                  "High",
                                  summary(ct1_mturk_fit)$coefficients[2,1],
                                  summary(ct1_mturk_fit)$coefficients[2,2])

# mexico low prej

ct1_mturk_fit <- glm(acceptscale_01 ~ skill,
                       data = ct1_mturk %>% filter(country == "Mexico",
                                             hisp_prej == "Low",
                                             info == 0))

ct1_mturk_co[nrow(ct1_mturk_co) + 1,] <- c("Mexico",
                                  "Low",
                                  summary(ct1_mturk_fit)$coefficients[2,1],
                                  summary(ct1_mturk_fit)$coefficients[2,2])

# Canada high prej

ct1_mturk_fit <- glm(acceptscale_01 ~ skill,
                       data = ct1_mturk %>% filter(country == "Canada",
                                             hisp_prej == "High",
                                             info == 0))

ct1_mturk_co[nrow(ct1_mturk_co) + 1,] <- c("Canada",
                                  "High",
                                  summary(ct1_mturk_fit)$coefficients[2,1],
                                  summary(ct1_mturk_fit)$coefficients[2,2])

# Canada low prej

ct1_mturk_fit <- glm(acceptscale_01 ~ skill,
                       data = ct1_mturk %>% filter(country == "Canada",
                                             hisp_prej == "Low",
                                             info == 0))

ct1_mturk_co[nrow(ct1_mturk_co) + 1,] <- c("Canada",
                                  "Low",
                                  summary(ct1_mturk_fit)$coefficients[2,1],
                                  summary(ct1_mturk_fit)$coefficients[2,2])


# GRAPH

ct1_mturk_co <- ct1_mturk_co %>%
  
  mutate(estimate = as.double(estimate)) %>% 
  
  mutate(se = as.double(se)) %>%
  
  mutate(lb = (estimate - (1.96 * se))) %>%
  
  mutate(ub = (estimate + (1.96 * se)))

ct1_mturk_co %>%
  
  group_by(prejudice, Country) %>%
  
  ggplot() +
  
  geom_pointrange(aes(x = prejudice, 
             y = estimate, 
             ymin = lb, 
             ymax = ub, 
             shape = Country,
             fill = Country),
             position = position_dodge(width=.5),
             size = 1) + 
  
  geom_hline(yintercept=0) + 
  
  labs(x = "Prejudice Level",
       y = "Skill Premium Afforded",
       title = "Critical Test 1 Analysis with Mechanical Turk Data") + 
  
  theme_classic()

```

We confirm the results of the original paper, showing that those with high 
levels of prejudice against hispanics afford a higher skill premium to Mexican
immigrants than they do white immigrants. While we don't reach the levels of 
significance of the original paper since we have overlapping error bars, the 
trend is at least directionally the same. We also reach significance in the 
amount of skill premium places on immigrants of different countries by 
individuals in the same population pool. 

# Critical Test 1 with Survey Sampling International Data

The analysis done here is largely the same as above but with a different set of 
data gathered later by the researchers. This data set was collected to affirm
the results of the mechanical turk data, and to ask additional questions 
relevant to critical test 4. 

```{r}

ct1_ssi <- ssi %>% 
  
  mutate(hisp_prej = (hispintel + hisplazy + hispviol) / 3) %>%
  
  dplyr::select(admitscale_01, skill, hisp_prej, mexico, sweden) %>%
  
  drop_na() %>%
  
  # we define low hisp prejudice to be below 2.5
  
  mutate(hisp_prej = ifelse(hisp_prej <= 2.5, "Low", "High")) %>%
  
  mutate(skill = factor(skill, labels = c("Low", "High"))) 

ct1_ssi_co <- data.frame(Country = character(),
                  prejudice = character(), 
                  estimate = double(),
                  se = double())

# mexico high prej

ct1_ssi_fit <- glm(admitscale_01 ~ skill,
                       data = ct1_ssi %>% filter(mexico == 1,
                                             hisp_prej == "High"))

ct1_ssi_co[nrow(ct1_ssi_co) + 1,] <- c("Mexico",
                                  "High",
                                  summary(ct1_ssi_fit)$coefficients[2,1],
                                  summary(ct1_ssi_fit)$coefficients[2,2])

# mexico low prej

ct1_ssi_fit <- glm(admitscale_01 ~ skill,
                       data = ct1_ssi %>% filter(mexico == 1,
                                             hisp_prej == "Low"))

ct1_ssi_co[nrow(ct1_ssi_co) + 1,] <- c("Mexico",
                                  "Low",
                                  summary(ct1_ssi_fit)$coefficients[2,1],
                                  summary(ct1_ssi_fit)$coefficients[2,2])

# sweden high prej

ct1_ssi_fit <- glm(admitscale_01 ~ skill,
                       data = ct1_ssi %>% filter(mexico == 0,
                                             hisp_prej == "High"))

ct1_ssi_co[nrow(ct1_ssi_co) + 1,] <- c("Sweden",
                                  "High",
                                  summary(ct1_ssi_fit)$coefficients[2,1],
                                  summary(ct1_ssi_fit)$coefficients[2,2])

# sweden low prej

ct1_ssi_fit <- glm(admitscale_01 ~ skill,
                       data = ct1_ssi %>% filter(mexico == 0,
                                             hisp_prej == "Low"))

ct1_ssi_co[nrow(ct1_ssi_co) + 1,] <- c("Sweden",
                                  "Low",
                                  summary(ct1_ssi_fit)$coefficients[2,1],
                                  summary(ct1_ssi_fit)$coefficients[2,2])

# GRAPH

ct1_ssi_co <- ct1_ssi_co %>%
  
  mutate(estimate = as.double(estimate)) %>% 
  
  mutate(se = as.double(se)) %>%
  
  mutate(lb = (estimate - (1.96 * se))) %>%
  
  mutate(ub = (estimate + (1.96 * se)))

ct1_ssi_co %>%
  
  group_by(prejudice, Country) %>%
  
  ggplot() +
  
  geom_pointrange(aes(x = prejudice, 
             y = estimate, 
             ymin = lb, 
             ymax = ub, 
             shape = Country,
             fill = Country),
             position = position_dodge(width=.5),
             size = 1) + 
  
  geom_hline(yintercept=0) + 
  
  labs(x = "Prejudice Level",
       y = "Skill Premium Afforded",
       title =  "Critical Test 1 Analysis with SSI Data") + 
  
  theme_classic()

```

The results here are consistent with the results derived in the original paper.
We see the same trend with high prejudice individuals having a higher skill 
premium for mexican immigrants than low prejudice individuals. This result 
continues to challenge the race neutral assumptions of previous literature. 

# Critical Test 2  with Mechanical Turk Data

For critical test 2, we segment respondents by their belief on whether the see
believe high or low skill immigrants are better (or if they see them equally). 
Here, we are looking for the same evidence of higher levels of a skill premium
for Mexican immigrants compared to white Canadian immigrants. 

```{r}

# Data Cleaning

ct2_mturk <- mturk %>% 
  
  dplyr::select(acceptscale_01, skill, info, country, skillbelief_01) %>%
  
  drop_na() %>%
  
  # we define high hisp prejudice to be below 3.5
  
  mutate(skillbelief = factor(skillbelief_01, labels = c("Low", 
                                                            "Equal", 
                                                            "High"))) %>%
  
  mutate(country = factor(country, labels = c("Canada", "Mexico"))) %>%
  
  mutate(skill = factor(skill, labels = c("Low", "High"))) 

# empty results
  
ct2_mturk_co <- data.frame(Country = character(),
                  skillbelief = character(), 
                  estimate = double(),
                  se = double())

# models

# mexico low

ct2_mturk_fit <- glm(acceptscale_01 ~ skill,
                       data = ct2_mturk %>% filter(country == "Mexico",
                                             skillbelief == "Low",
                                             info == 0))

ct2_mturk_co[nrow(ct2_mturk_co) + 1,] <- c("Mexico",
                                  "Low Skill",
                                  summary(ct2_mturk_fit)$coefficients[2,1],
                                  summary(ct2_mturk_fit)$coefficients[2,2])

# mexico equal

ct2_mturk_fit <- glm(acceptscale_01 ~ skill,
                       data = ct2_mturk %>% filter(country == "Mexico",
                                             skillbelief == "Equal",
                                             info == 0))

ct2_mturk_co[nrow(ct2_mturk_co) + 1,] <- c("Mexico",
                                  "Equal",
                                  summary(ct2_mturk_fit)$coefficients[2,1],
                                  summary(ct2_mturk_fit)$coefficients[2,2])

# mexico high

ct2_mturk_fit <- glm(acceptscale_01 ~ skill,
                       data = ct2_mturk %>% filter(country == "Mexico",
                                             skillbelief == "High",
                                             info == 0))

ct2_mturk_co[nrow(ct2_mturk_co) + 1,] <- c("Mexico",
                                  "High Skill",
                                  summary(ct2_mturk_fit)$coefficients[2,1],
                                  summary(ct2_mturk_fit)$coefficients[2,2])

# Canada Low

ct2_mturk_fit <- glm(acceptscale_01 ~ skill,
                       data = ct2_mturk %>% filter(country == "Canada",
                                             skillbelief == "Low",
                                             info == 0))

ct2_mturk_co[nrow(ct2_mturk_co) + 1,] <- c("Canada",
                                  "Low Skill",
                                  summary(ct2_mturk_fit)$coefficients[2,1],
                                  summary(ct2_mturk_fit)$coefficients[2,2])

# Canada Equal

ct2_mturk_fit <- glm(acceptscale_01 ~ skill,
                       data = ct2_mturk %>% filter(country == "Canada",
                                             skillbelief == "Equal",
                                             info == 0))

ct2_mturk_co[nrow(ct2_mturk_co) + 1,] <- c("Canada",
                                  "Equal",
                                  summary(ct2_mturk_fit)$coefficients[2,1],
                                  summary(ct2_mturk_fit)$coefficients[2,2])

# Canada High

ct2_mturk_fit <- glm(acceptscale_01 ~ skill,
                       data = ct2_mturk %>% filter(country == "Canada",
                                             skillbelief == "High",
                                             info == 0))

ct2_mturk_co[nrow(ct2_mturk_co) + 1,] <- c("Canada",
                                  "High Skill",
                                  summary(ct2_mturk_fit)$coefficients[2,1],
                                  summary(ct2_mturk_fit)$coefficients[2,2])

# Pooled Low

ct2_mturk_fit <- glm(acceptscale_01 ~ skill,
                       data = ct2_mturk %>% filter(
                                             skillbelief == "Low",
                                             info == 0))

ct2_mturk_co[nrow(ct2_mturk_co) + 1,] <- c("Pooled",
                                  "Low Skill",
                                  summary(ct2_mturk_fit)$coefficients[2,1],
                                  summary(ct2_mturk_fit)$coefficients[2,2])

# Pooled Equal

ct2_mturk_fit <- glm(acceptscale_01 ~ skill,
                       data = ct2_mturk %>% filter(
                                             skillbelief == "Equal",
                                             info == 0))

ct2_mturk_co[nrow(ct2_mturk_co) + 1,] <- c("Pooled",
                                  "Equal",
                                  summary(ct2_mturk_fit)$coefficients[2,1],
                                  summary(ct2_mturk_fit)$coefficients[2,2])

# ooled High

ct2_mturk_fit <- glm(acceptscale_01 ~ skill,
                       data = ct2_mturk %>% filter(
                                             skillbelief == "High",
                                             info == 0))

ct2_mturk_co[nrow(ct2_mturk_co) + 1,] <- c("Pooled",
                                  "High Skill",
                                  summary(ct2_mturk_fit)$coefficients[2,1],
                                  summary(ct2_mturk_fit)$coefficients[2,2])

# GRAPH

ct2_mturk_co <- ct2_mturk_co %>%
  
  mutate(estimate = as.double(estimate)) %>% 
  
  mutate(se = as.double(se)) %>%
  
  mutate(lb = (estimate - (1.96 * se))) %>%
  
  mutate(ub = (estimate + (1.96 * se)))

ct2_mturk_co %>%
  
  group_by(skillbelief, Country) %>%
  
  ggplot() +
  
  geom_pointrange(aes(x = skillbelief, 
             y = estimate, 
             ymin = lb, 
             ymax = ub, 
             shape = Country,
             fill = Country),
             position = position_dodge(width=.5)) + 
  
  geom_hline(yintercept=0) + 
  
  labs(x = "Type of Immigrant Prefered",
       y = "Skill Premium Afforded",
       title = "Critical Test 1 Reanalysis") + 
  
  theme_classic()

```

We again confirm the results of the original paper. Among all groups, the highest
skill premium is given to Mexican immigrants, meaning across all groups they 
care most about Mexicans being high skill than Canadian immigrants. Additionally,
even the group that says they prefer low skilled immigrants still affords a 
significant skill premium to all immigrants. This further supports the papers 
conclusion that Americans have a higher skill bar for Latino immigrants than 
they do for white immigrants, challenging the race neutral conclusions of
previous papers. 

# Critical Test 2 with SSI Data

Here, we repeat the above analysis but with the SSI data. 

```{r}

ct2_ssi <- ssi %>% 
  
  
  dplyr::select(admitscale_01, skill, mexico, sweden, skillbelief) %>%
  
  drop_na() %>%
  
  # we define low hisp prejudice to be below 2.5
  
  mutate(skillbelief = factor(skillbelief, labels = c("Low", "High"))) %>%
  
  mutate(skill = factor(skill, labels = c("Low", "High"))) 

ct2_ssi_co <- data.frame(Country = character(),
                  skillbelief = character(), 
                  estimate = double(),
                  se = double())

# MODELS

# mexico low

ct2_ssi_fit <- glm(admitscale_01 ~ skill,
                       data = ct2_ssi %>% filter(mexico == 1,
                                             skillbelief == "Low"))

ct2_ssi_co[nrow(ct2_ssi_co) + 1,] <- c("Mexico",
                                  "Low Skill",
                                  summary(ct2_ssi_fit)$coefficients[2,1],
                                  summary(ct2_ssi_fit)$coefficients[2,2])

# mexico high

ct2_ssi_fit <- glm(admitscale_01 ~ skill,
                       data = ct2_ssi %>% filter(mexico == 1,
                                             skillbelief == "High"))

ct2_ssi_co[nrow(ct2_ssi_co) + 1,] <- c("Mexico",
                                  "High Skill",
                                  summary(ct2_ssi_fit)$coefficients[2,1],
                                  summary(ct2_ssi_fit)$coefficients[2,2])

# sweden low

ct2_ssi_fit <- glm(admitscale_01 ~ skill,
                       data = ct2_ssi %>% filter(mexico == 0,
                                             skillbelief == "Low"))

ct2_ssi_co[nrow(ct2_ssi_co) + 1,] <- c("Sweden",
                                  "Low Skill",
                                  summary(ct2_ssi_fit)$coefficients[2,1],
                                  summary(ct2_ssi_fit)$coefficients[2,2])

# sweden high

ct2_ssi_fit <- glm(admitscale_01 ~ skill,
                       data = ct2_ssi %>% filter(mexico == 0,
                                             skillbelief == "High"))

ct2_ssi_co[nrow(ct2_ssi_co) + 1,] <- c("Sweden",
                                  "High Skill",
                                  summary(ct2_ssi_fit)$coefficients[2,1],
                                  summary(ct2_ssi_fit)$coefficients[2,2])

# pooled low

ct2_ssi_fit <- glm(admitscale_01 ~ skill,
                       data = ct2_ssi %>% filter(
                                             skillbelief == "Low"))

ct2_ssi_co[nrow(ct2_ssi_co) + 1,] <- c("Pooled",
                                  "Low Skill",
                                  summary(ct2_ssi_fit)$coefficients[2,1],
                                  summary(ct2_ssi_fit)$coefficients[2,2])

# pooled high

ct2_ssi_fit <- glm(admitscale_01 ~ skill,
                       data = ct2_ssi %>% filter(
                                             skillbelief == "High"))

ct2_ssi_co[nrow(ct2_ssi_co) + 1,] <- c("Pooled",
                                  "High Skill",
                                  summary(ct2_ssi_fit)$coefficients[2,1],
                                  summary(ct2_ssi_fit)$coefficients[2,2])

# GRAPH

ct2_ssi_co <- ct2_ssi_co %>%
  
  mutate(estimate = as.double(estimate)) %>% 
  
  mutate(se = as.double(se)) %>%
  
  mutate(lb = (estimate - (1.96 * se))) %>%
  
  mutate(ub = (estimate + (1.96 * se)))

ct2_ssi_co %>%
  
  group_by(skillbelief, Country) %>%
  
  ggplot() +
  
  geom_pointrange(aes(x = skillbelief, 
             y = estimate, 
             ymin = lb, 
             ymax = ub, 
             shape = Country,
             fill = Country),
             position = position_dodge(width=.5)) + 
  
  geom_hline(yintercept=0) + 
  
  labs(x = "Type of Immigrant Prefered",
       y = "Skill Premium Afforded",
       title = "Critical Test 1 Reanalysis") + 
  
  theme_classic()

```

In this analysis, we reach the same results as the original paper, in which
the results from the regression show the opposite of what is shown in 
the original paper, in that a lower skill premium is afforded for Mexican
immigrants. However, the original paper completely ignores this result, not 
mentioning the results of this regression at all. This raises some red flags for
me, as while these results still show that there is a racial component to the 
skill premium, this model has the opposite conclusion that the authors have
in that respondents require a higher level of skill from white immigrants. 

# Conclusion

## Results of the replication

We found in our replication of the original authors results that we largely 
agree with the conclusion they reached. There is a rather clear ethnic
component in the skill premium, with it seeming that prejudices against
low skilled Latino immigrants has caused Americans to give consider skill
more for that group then they do with immigrants from majority white countries.
However, while the results in both 3B of the original paper and our analysis 
of critical test 2 with the ssi data both show that the bias is in the opposite 
direction, it still demonstrates a racial bias, inconsistent with the arguments
in previous papers. 

## Possible extensions

The data sets gathered by the studies conducted by the authors offer
opportunities to study prejudice beyond it's effects on the skill premium. 
It would be interesting to look at prejudice as a function of education and 
income, and look at the interplay of these variables and how an individual 
evaluates a given individual. Also, investigating whether 
there other "premiums", such as with age or gender. These analysis could 
offer an interesting perspective on how Americans evaluate immigrants, which
could impact political messaging, legislation, and education. 

# References

1. Newman, Benjamin J. and Malhotra, Neil. 2019. "Economic Reasoning with a 
Racial Hue: Is the Immigration Consensus Purely Race Neutral?" 
The Journal of Politics 2019 81(1), 153-166
2. Hainmueller, Jens, and Daniel J. Hopkins. 2015. “The Hidden American
Immigration Consensus: A Conjoint Analysis of Attitudes toward
Immigrants.” American Journal of Political Science 59 (3): 529–48.
3. Wright, Matthew, Morris Levy, and Jack Citrin. 2016. “Public Attitudes
toward Immigration Policy across the Legal/Illegal Divide: The Role of
Categorical and Attribute-Based Decision-Making.” Political Behavior
38 (1): 229–53.

## Code Repository






























